The Effect of Void on the

### 2018-10-04 draft/alexpub.tex
no

% Full title of the paper (Capitalized)
% \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
\Title{On the Cold Deformation Behaviour of Two Phase TiAl Alloy with and without Void Defects}
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/disl2-gamma}
		\label{fig:surf}
		\caption{stress-strain curve}
	\end{figure}
1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface. This may significantly reduce the Schmid factor and thus impede slip transfer. At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree. Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.

>>>>

% Full title of the paper (Capitalized)
% \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha$($\rm Ti_3Al$) Alloy}
\Title{The Effect of Void on the}
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

@@

%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=1\linewidth]{img/disl2-gamma}
%		\label{fig:surf}
%		\caption{stress-strain curve}
%	\end{figure}
1.In many cases the orientation of slip slip is changed because the crystallographically available slip and directions are not continuous across the interface. This may significantly reduce the Schmid factor and thus impede slip transfer. At the $\gamma/\gamma$ interfaces the orientation of the slip plan could change through a relevantly large angle of about 90 degree. Reorientation of slip is always required at the $\alpha_{2}/\gamma$ interface; the smallest angle between the corresponding slip planes ${1 1 1 }_{\gamma}$ and ${ 1 0 -1 0}_{\alpha_2}$ is about 19 degree \cite{}.
